\begin{thebibliography}{99}
\bibitem{ref1} Proakis, John G., et al. Communication systems engineering. Vol. 2. New Jersey: Prentice Hall, 1994.
\bibitem{ref2} Bahai, Ahmad RS, Burton R. Saltzberg, and Mustafa Ergen. Multi-carrier digital communications: theory and applications of OFDM. Springer Science \& Business Media, 2004.
\bibitem{ref3} Yang, Lie-Liang. Multicarrier communications. John Wiley \& Sons, 2009.
\bibitem{ref4} Liu, Hui, and Guoqing Li. OFDM-based broadband wireless networks: design and optimization. John Wiley \& Sons, 2005.
\bibitem{ref5} Hara, Shinsuke, and Ramjee Prasad. Multicarrier techniques for 4G mobile communications. Artech House, 2003.
\bibitem{ref9} Chi, Cheng, and Zhaohui Li. "Design of modulated excitation waveform based on OFDM signals for medical ultrasound imaging." 2014 12th International Conference on Signal Processing (ICSP). IEEE, 2014.
\bibitem{ref6} Electronics Notes. What is OFDM: Orthogonal Frequency Division Multiplexing. Available at: \url{https://www.electronics-notes.com/articles/radio/multicarrier-modulation/ofdm-orthogonal-frequency-division-multiplexing-what-is-tutorial-basics.php}, access in 19 apr. 2021.
\bibitem{ref7} Keysight. Concepts of Orthogonal Frequency Division Multiplexing (OFDM) and 802.11 WLAN. Available at: \url{http://rfmw.em.keysight.com/wireless/helpfiles/89600b/webhelp/subsystems/wlan-ofdm/Content/ofdm\_basicprinciplesoverview.htm}, access in 19 apr. 2021
\bibitem{ref8} Bob Witte. The basics of 5G’s modulation, OFDM. Available at: \url{https://www.5gtechnologyworld.com/the-basics-of-5gs-modulation-ofdm/}, access in 19 apr. 2021.



\end{thebibliography}