\begin{thebibliography}{99}
\bibitem{abdoli2015filtered} Abdoli, Javad, Ming Jia, and Jianglei Ma. "Filtered OFDM: A new waveform for future wireless systems." 2015 IEEE 16th International Workshop on Signal Processing Advances in Wireless Communications (SPAWC). IEEE, 2015.

\bibitem{cheng2016filtered} Cheng, Xudong, et al. "A filtered OFDM using FIR filter based on window function method." 2016 IEEE 83rd Vehicular Technology Conference (VTC Spring). IEEE, 2016.

\bibitem{zhang2015filtered} Zhang, Xi, et al. "Filtered-OFDM-enabler for flexible waveform in the 5th generation cellular networks." 2015 IEEE Global Communications Conference (GLOBECOM). IEEE, 2015.

\bibitem{zhang2017filtered} Zhang, Lei, et al. "Filtered OFDM systems, algorithms, and performance analysis for 5G and beyond." IEEE Transactions on Communications 66.3 (2017): 1205-1218.

\bibitem{de2019comparing} de Figueiredo, Felipe AP, et al. "Comparing f-OFDM and OFDM performance for MIMO systems considering a 5G scenario." 2019 IEEE 2nd 5G World Forum (5GWF). IEEE, 2019.

\bibitem{al2020improving} Al‐Jawhar, Yasir Amer, et al. "Improving PAPR performance of filtered OFDM for 5G communications using PTS." ETRI Journal (2020).

\bibitem{ece489} ECE 489 -- Communications Systems Laboratory. OFDM modulation. New Jersey Institute of Technology, 2018. Available at \url{http://ecelabs.njit.edu/ece489v2}, last accessed apr. 25, 2021.

\bibitem{wen2009hanning} Wen, He, et al. "Hanning self-convolution window and its application to harmonic analysis." Science in China Series E: Technological Sciences 52.2 (2009): 467-476.


\end{thebibliography}